---
title: "Chagas Meta-analysis: benznidazole and fosravuconazole"
author: "James Watson"
format: html
editor: visual
---

```{r}
knitr::opts_chunk$set(cache = F, cache.comments = FALSE,
                      echo = T, include = TRUE, 
                      fig.width = 8, fig.height = 8,
                      fig.pos = 'H',dev = 'png', dpi = 300)

library(RColorBrewer)
library(tidyverse)
# library(cmdstanr)
library(rstan)
# library(posterior)
library(bayesplot)
library(gridExtra)
library(survival)
library(survminer)


source('functions.R')
# source('make_adam.R')

RE_RUN_STAN_MODEL=T
options(mc.cores = parallel::detectCores())
rstan_options(auto_write = TRUE)


```

Theoretical considerations around sensitivity. We assume the number of parasites in a given blood sample are Poisson distributed.

```{r theoretical_sensitivity, fig.width=10}
library(expint)
# probability that the max of k independent poisson draws is zero is given by the incomplete
# gamma function
my_lambdas = seq(from=log10(1/5000), to=log10(5000/5000),length.out=100)
par(las=1, cex.lab=1.3, cex.axis=1.3)
# 15 independent draws
plot(my_lambdas, 1-expint::gammainc(1,5*(10^my_lambdas))^15,
     type='l', panel.first=grid(), xaxt='n',
     xlab='Parasite density per ml',
     ylab='Probability at least one draw has at least 1 parasite',lwd=3, col='darkred')
vals = c(0.0002, 0.001, 0.01, .1, 1, 10)
axis(1, at = log10(vals),labels = vals)
abline(h=0.5,lty=2)
# 30 independent draws
lines(my_lambdas, 1-expint::gammainc(1,5*(10^my_lambdas))^30,
      lty=1,lwd=3,col='grey')

# 5 independent draws
lines(my_lambdas, 1-expint::gammainc(1,5*(10^my_lambdas))^5,
      lty=2,lwd=3,col='darkblue')
# single draw
lines(my_lambdas, 1-expint::gammainc(1,5*(10^my_lambdas)),
      lty=3,lwd=2)

legend('topleft', legend = c(30, 15, 5, 1), title = 'n draws',
       lwd=3, lty=c(1,1,2,3), col=c('grey','darkred', 'darkblue','black'), inset = 0.03, cex=1.5)
```

## *Load data*

```{r}
load('RData/pcr_chagas.RData')
```

## *Plot PCR data*

*Triplicates*

```{r heterosckedasticity, fig.height=8, fig.width=12}
pcr_chagas = pcr_chagas %>% 
  group_by(USUBJID, Day_frm_rand, MBREFID) %>%
  mutate(
    CT = ifelse(CT<25, NA, CT),
    repeats = sum(!is.na(CT)),
    CT_mean_sample = mean(CT,na.rm = T),
    CT_sd_sample = sd(CT,na.rm=T),
    n_40 = sum(CT==40,na.rm = T)
  ) %>% ungroup() %>%
  filter(!is.na(CT))

pcr_chagas_trip = pcr_chagas %>% 
  filter(repeats==3, n_40<3) %>%
  distinct(USUBJID, Day_frm_rand, MBREFID, .keep_all = T)
pcr_chagas_trip %>%
  ggplot(aes(x=CT_mean_sample, y=CT_sd_sample,
             color=as.factor(n_40)))+
  geom_point()+
  geom_smooth(data = filter(pcr_chagas_trip, n_40==0, CT_mean_sample<36),
              colour="black", linewidth=2)+
  theme_minimal()+
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=16,face="bold"))+
  xlab('Mean CT value across triplicates')+
  ylab('Standard deviation of CT values')+
  labs(color='CT=40') 

```

### *prep data*

Define a per protocol set of individuals. 80% of dose taken or 80% of duration (day of last dose)

```{r per_protocol}
pcr_chagas = pcr_chagas %>% 
  group_by(ARM) %>%
  mutate(
    BNZ_total_dose_allocated = case_when(
      ARM=='BNZ 300MG 8W' ~ 8*7*300,
      ARM=='BNZ 300MG 4W' ~ 4*7*300,
      ARM=='BNZ 300MG 2W' ~ 2*7*300,
      ARM=='BNZ 300MG/WK + E1224 300MG 8W' ~ 8*300,
      ARM=='BNZ 150MG 4W + E1224 300MG 8W' ~ 4*7*150,
      ARM=='BNZ 150MG 4W' ~ 4*7*150,
      T ~ 0
    ),
    BNZ_total_duration_allocated = case_when(
      ARM=='BNZ 300MG 8W' ~ 8*7,
      ARM=='BNZ 300MG 4W' ~ 4*7,
      ARM=='BNZ 300MG 2W' ~ 2*7,
      ARM=='BNZ 300MG/WK + E1224 300MG 8W' ~ 8*7,
      ARM=='BNZ 150MG 4W + E1224 300MG 8W' ~ 4*7,
      ARM=='BNZ 150MG 4W' ~ 4*7,
      T ~ 0
    )
  ) %>%
  group_by(USUBJID) %>%
  mutate(
    PP_pop1 = BNZ_total_dose >= 0.8*BNZ_total_dose_allocated,
    PP_pop2 = BNZ_total_days >= 0.8*BNZ_total_duration_allocated)
```

```{r}
# make summaries by sample, visit and baseline values
# MBREFID indicates the blood sample
# MBGRPID indicates the technical replicate

pcr_chagas = pcr_chagas %>% 
  group_by(USUBJID, Day_frm_rand, MBREFID) %>%
  mutate(
    N_technical_replicates = 1:n()) %>%
  ungroup() %>%
  filter(N_technical_replicates<=3) %>%
  mutate(N_pos_sample = sum(CT<40)) %>%
  group_by(USUBJID,Day_frm_rand) %>% 
  arrange(USUBJID, Day_frm_rand, MBREFID, MBGRPID) %>%
  mutate(PCR_number = 1:n()) %>%
  ungroup() %>% 
  group_by(USUBJID,Day_frm_rand) %>%
  mutate(percent_pos = sum(CT<40)/length(CT),
         Any_Pos_40 = any(CT<40),
         N_PCRs = max(PCR_number),
         N_pos = sum(CT<40)) %>%
  group_by(USUBJID) %>%
  mutate(
    Percent_pos_baseline = mean(CT[Day_frm_rand<=0] < 40),
    Mean_CT_inv_baseline = 40-mean(CT[Day_frm_rand<=0]),
    N_FUP_VISITS = length(unique(Day_frm_rand[which(Day_frm_rand>EOT)])),
    Day_last_Visit = max(Day_frm_rand)) %>%
  ungroup() %>%
  filter(PCR_number<=9) %>%
  arrange(STUDYID, ARM, Mean_CT_inv_baseline, Percent_pos_baseline,
          USUBJID, VISIT_numeric, PCR_number)

FUP_dat = pcr_chagas %>% filter(Day_frm_rand>EOT) %>%
  group_by(USUBJID) %>%
  mutate(Fail = any(CT<40),
         N_Fail = sum(CT<40),
         min_Fail = min(CT),
         N_PCRs_FUP = n()) %>% ungroup() %>%
distinct(USUBJID,.keep_all = T) %>% select(USUBJID, ARM, Fail, N_Fail, N_PCRs,min_Fail)

table(FUP_dat$ARM, FUP_dat$Fail)
table(FUP_dat$ARM, FUP_dat$N_Fail==1)
table(FUP_dat$ARM, FUP_dat$N_Fail==1 & FUP_dat$min_Fail>=38)


screen_fails = pcr_chagas %>% filter(ARM=='FAILED SCREENING')
pcr_chagas = pcr_chagas %>% filter(!ARM=='FAILED SCREENING')

dat_summary_visits = pcr_chagas %>% distinct(USUBJID, Day_frm_rand, .keep_all = T)
dat_summary = pcr_chagas %>% 
  group_by(USUBJID) %>%
  mutate(FUP_time = max(Day_frm_rand) - min(Day_frm_rand)) %>%
  distinct(USUBJID, .keep_all = T)

sum(dat_summary$FUP_time)/365

table(dat_summary$ARM, dat_summary$PP_pop1)

table(dat_summary$STUDYID, dat_summary$SITEID)
mean(dat_summary$SEX=='F')
table(dat_summary$ARM, dat_summary$STUDYID)
table(dat_summary$N_FUP_VISITS)

table(dat_summary$ARM, dat_summary$BNZ_total_days)
```

### patients failed screening

```{r}
screen_fails = screen_fails %>% group_by(USUBJID) %>%
  mutate(N_pos = sum(CT<40),
         N_PCRs = n()) %>%
  distinct(USUBJID, .keep_all = T)
table(screen_fails$STUDYID, screen_fails$N_pos==0)
```

```{r pcr_plot, fig.width=15, fig.height=12}
my_breaks = c(10, 30, 34, 36, 38, 39.99999,40)
my_breaks_legend = c('<30','30-34','34-36','36-38','38-40','>=40')
my_cols = c(brewer.pal(11, 'RdYlBu')[c(1,2,4,9,11)],brewer.pal(9, 'Pastel1')[9])

for(ss in unique(pcr_chagas$STUDYID)){
  pcr_chagas_ss=pcr_chagas %>% filter(STUDYID==ss)
  writeLines(sprintf('In the %s trial there are %s PCR measurements',
                     ss,nrow(pcr_chagas_ss)))
  pcr_mat = make_matrix_pcr(pcr_dat = pcr_chagas_ss,
                            N_max_PCR = 9)
  
  writeLines(sprintf('In the pcr matrix for %s trial there are %s PCR measurements',
                     ss,sum(!is.na(pcr_mat)) ))
  
  
  par(mar=c(3,8,1,8))
  xx2 = pcr_chagas_ss %>% ungroup %>% distinct(USUBJID,.keep_all = T)
  ind_y = which(!duplicated(xx2$ARM))
  plot_pcr_matrix(pcr_mat = pcr_mat,
                  my_breaks = my_breaks, 
                  my_break_legend = my_breaks_legend,
                  my_cols = my_cols,
                  arm_labels = unique(pcr_chagas_ss$ARM),
                  h_lines_ind = ind_y[-1]-0.5,
                  y_lab_ind = ind_y + diff(c(ind_y, nrow(pcr_mat)+1))/2)
}
```

*placebo individuals in E1224 and BENDITA studies*

```{r placebos, fig.height=6, fig.width=12}
visits_overlap = intersect(unique(pcr_chagas$VISIT_numeric[pcr_chagas$STUDYID=='BENDITA']),
                           unique(pcr_chagas$VISIT_numeric[pcr_chagas$STUDYID=='E1224']))

pcr_chagas_ss=pcr_chagas %>% 
  filter(ARM == 'PLACEBO',
         VISIT_numeric %in% visits_overlap)
pcr_mat = make_matrix_pcr(pcr_dat = pcr_chagas_ss,N_max_PCR = 9)

par(mar=c(5,5,0.5,0.5))
xx2 = pcr_chagas_ss %>% ungroup %>% distinct(USUBJID,.keep_all = T)
ind_y = which(!duplicated(xx2$STUDYID))
plot_pcr_matrix(pcr_mat = pcr_mat,
                my_breaks = my_breaks, 
                my_break_legend = my_breaks_legend,
                my_cols = my_cols,
                arm_labels = c('BENDITA','E1224'),
                h_lines_ind = ind_y[-1]-0.5,
                y_lab_ind = ind_y + diff(c(ind_y, nrow(pcr_mat)+1))/2)
```

*two versus eight weeks*

```{r two_vs_eight, fig.height=6, fig.width=12}
pcr_chagas_ss=pcr_chagas %>% 
  filter(STUDYID %in% c('BENDITA'),
         ARM %in% c('BNZ 300MG 2W',
                    'BNZ 300MG 8W'))
pcr_mat = make_matrix_pcr(pcr_dat = pcr_chagas_ss,N_max_PCR = 9)

par(mar=c(4,7,0.5,0.5))
xx2 = pcr_chagas_ss %>% ungroup %>% distinct(USUBJID,.keep_all = T)
ind_y = which(!duplicated(xx2$ARM))
plot_pcr_matrix(pcr_mat = pcr_mat,
                my_breaks = my_breaks, 
                my_break_legend = my_breaks_legend,
                my_cols = my_cols,
                arm_labels = c('BNZ 2 weeks','BNZ 8 weeks'),
                h_lines_ind = ind_y[-1]-0.5,
                y_lab_ind = ind_y + diff(c(ind_y, nrow(pcr_mat)+1))/2)

```

*Weekly benznidazole works really well!*

```{r weekly_bnz, fig.height=6, fig.width=12}
pcr_chagas_ss=pcr_chagas %>% 
  filter(ARM %in% c("BNZ 300MG/WK + E1224 300MG 8W",
                    "E1224 200MG 8W",
                    "E1224 400MG 8W"),
         VISIT_numeric %in% visits_overlap)
pcr_mat = make_matrix_pcr(pcr_dat = pcr_chagas_ss,N_max_PCR = 9)

par(mar=c(5,8,0.5,6))
xx2 = pcr_chagas_ss %>% ungroup %>% distinct(USUBJID,.keep_all = T)
ind_y = which(!duplicated(xx2$ARM))
plot_pcr_matrix(pcr_mat = pcr_mat,
                my_breaks = my_breaks, 
                my_break_legend = my_breaks_legend,
                my_cols = my_cols,
                arm_labels = unique(pcr_chagas_ss$ARM),
                h_lines_ind = ind_y[-1]-0.5,
                y_lab_ind = ind_y + diff(c(ind_y, nrow(pcr_mat)+1))/2)
```

*BNZ 150 for 4 weeks*

```{r bnz_150_4wks, fig.height=10, fig.width=12}
pcr_chagas_ss=pcr_chagas %>% 
  filter(STUDYID %in% c('BENDITA'),
         ARM %in% c('BNZ 150MG 4W'))
pcr_mat = make_matrix_pcr(pcr_dat = pcr_chagas_ss,N_max_PCR = 9)

par(mar=c(2,7,0.5,0.5))
xx2 = pcr_chagas_ss %>% ungroup %>% distinct(USUBJID,.keep_all = T)
ind_y = which(!duplicated(xx2$ARM))
plot_pcr_matrix(pcr_mat = pcr_mat,
                my_breaks = my_breaks, 
                my_break_legend = my_breaks_legend,
                my_cols = my_cols,
                arm_labels = unique(pcr_chagas_ss$USUBJID),
                h_lines_ind = ind_y[-1]-0.5,
                y_lab_ind = 1:nrow(pcr_mat),cex_y_lab = .7)

# View(dat_summary %>% filter(USUBJID %in% c('BENDITA_466','BENDITA_594')))

```

*Order individuals by how many days BNZ and by total mg/kg dose*

```{r days_bnz, fig.width=10, fig.height=8}
pcr_chagas_ss = pcr_chagas %>%
  filter(BNZ_total_days<=14,BNZ_total_days>0) %>%
  arrange(desc(BNZ_total_dose_mg_kg),desc(BNZ_total_days), 
          Mean_CT_inv_baseline, Day_frm_rand)
pcr_mat = make_matrix_pcr(pcr_dat = pcr_chagas_ss,N_max_PCR = 9)

pcr_chagas_ss_summary = pcr_chagas_ss %>% distinct(USUBJID,.keep_all = T)%>%
  select(USUBJID, STUDYID, ARM, BNZ_total_days, BNZ_total_dose_mg_kg, weight, BNZ_total_dose)

par(mar=c(3,3,0.5,4),las=1)
xx2 = pcr_chagas_ss %>% ungroup %>% distinct(USUBJID,.keep_all = T)
ind_y = which(!duplicated(xx2$BNZ_total_days))
plot_pcr_matrix(pcr_mat = pcr_mat,
                my_breaks = my_breaks, 
                my_break_legend = my_breaks_legend,
                my_cols = my_cols,
                arm_labels = round(pcr_chagas_ss_summary$BNZ_total_dose_mg_kg,1),
                h_lines_ind = NULL,
                y_lab_ind = 1:nrow(pcr_chagas_ss_summary),
                cex_y_lab = .7, 
                plot_legend = F)
axis(4, at = 1:nrow(pcr_chagas_ss_summary), labels = pcr_chagas_ss_summary$BNZ_total_days, cex.axis=.7)
```

*Possible sample mix-up, this is identifiable using this graphical visualisation*

```{r mix_up, fig.height=10, fig.width=12}
pcr_chagas_ss=pcr_chagas %>% 
  filter(STUDYID %in% c('BENDITA'),
         ARM %in% c('PLACEBO',
                    'BNZ 300MG 4W'))
pcr_mat = make_matrix_pcr(pcr_dat = pcr_chagas_ss,N_max_PCR = 9)

par(mar=c(2,7,0.5,0.5))
xx2 = pcr_chagas_ss %>% ungroup %>% distinct(USUBJID,.keep_all = T)
ind_y = which(!duplicated(xx2$ARM))
plot_pcr_matrix(pcr_mat = pcr_mat,
                my_breaks = my_breaks, 
                my_break_legend = my_breaks_legend,
                my_cols = my_cols,
                arm_labels = unique(pcr_chagas_ss$USUBJID),
                h_lines_ind = ind_y[-1]-0.5,
                y_lab_ind = 1:nrow(pcr_mat),cex_y_lab = .7)

# View(dat_summary %>% filter(USUBJID %in% c('BENDITA_466','BENDITA_594')))

```

## *Quantitative analysis*

### *cumulative probabilities*

*cumulative distributions of the qPCR CT values in individuals with + PCR during follow-up*

```{r cum_CT_values_FUP}
xlims=c(28,40)
xs=seq(28,40, by=.1)

pcr_chagas_ss = pcr_chagas %>% 
  filter(VISIT_numeric>EOT,
         STUDYID=='BENDITA', 
         !USUBJID %in% '681',
         ARM!='PLACEBO',CT<40) 
par(las=1)
plot(xs, 1-ecdf(pcr_chagas_ss$CT)(xs), main='BENDITA', xlab='CT', 
     ylab = 'Cumulative probability',panel.first=grid(),
     xlim=xlims,type='l',lwd=2)
text(x = 38,y=0.7,paste(round(100*(1-ecdf(pcr_chagas_ss$CT)(36))),'%',sep=''),cex=1.5)
abline(v=36,lty=2)
for(aa in unique(pcr_chagas_ss$ARM)){
  pcr_chagas_ss_aa = pcr_chagas_ss%>%filter(ARM==aa)
  lines(xs, 1-ecdf(pcr_chagas_ss_aa$CT)(xs))
}

pcr_chagas_ss = pcr_chagas %>% 
  filter(VISIT_numeric>EOT,
         STUDYID=='E1224', 
         !ARM%in%c('PLACEBO',"BNZ 300MG 8W"),
         CT<40) 
par(las=1)
plot(xs, 1-ecdf(pcr_chagas_ss$CT)(xs), main='E1224', xlab='CT', 
     ylab = 'Cumulative probability',panel.first=grid(),
     xlim=xlims,type='l',lwd=2)
text(x = 38,y=0.7,paste(round(100*(1-ecdf(pcr_chagas_ss$CT)(36))),'%',sep=''),cex=1.5)
abline(v=36,lty=2)

pcr_chagas_ss = pcr_chagas %>% 
  filter(VISIT_numeric>EOT,
         ARM%in%c('PLACEBO'),
         CT<40) 
par(las=1)
plot(xs, 1-ecdf(pcr_chagas_ss$CT)(xs), main='PLACEBO', xlab='CT', 
     ylab = 'Cumulative probability',panel.first=grid(),
     xlim=xlims,type='l',lwd=2)
text(x = 38,y=0.7,paste(round(100*(1-ecdf(pcr_chagas_ss$CT)(36))),'%',sep=''),cex=1.5)
abline(v=36,lty=2)
```

### *rough failure estimates*

```{r failure_proportions, fig.width=12, fig.height=8}
strong_fail = 38
summary_outcomes = pcr_chagas %>%
  filter(!is.na(CT), Day_frm_rand>EOT) %>%
  group_by(USUBJID, VISIT) %>%
  mutate(N_PCRs = length(CT),
         N_pos = sum(CT < 40),
         N_weak_pos = sum(CT>strong_fail & CT<40),
         Borderline_pos = (N_pos==1 & N_weak_pos==1)) %>%
  distinct(USUBJID, VISIT, .keep_all = T) %>%
  group_by(USUBJID) %>%
  mutate(
    N_fup_visits = length(N_PCRs),
    N_fup_pcrs = sum(N_PCRs),
    N_pos_tot = sum(N_pos),
    N_weak_pos_tot = sum(N_weak_pos)) %>%
  distinct(USUBJID, .keep_all = T) %>%
  filter(N_fup_visits>1)

xx=summary_outcomes %>% group_by(ARM) %>%
  summarise(
    N = length(N_pos_tot),
    `FUP Visits` = median(N_fup_visits),
    Fail = sum(N_pos_tot>0),
    `Weak Fail` = sum(N_weak_pos_tot==1 & N_pos_tot==1),
    `Strong Fail` = Fail- `Weak Fail`,
    `Percent Fail` = round(100*Fail/N),
    `Percent Strong Fail` = round(100*`Strong Fail`/N)
  ) %>% arrange(`Percent Strong Fail`)
xx

require(DescTools)
par(mar=c(10,5,1,1),las=1, cex.axis=1.3, cex.lab=1.3)
plot(1:nrow(xx), xx$`Percent Fail`, ylim=c(0,100),panel.first = grid(),
     xaxt='n', xlab='', ylab='Failure (%)',pch=15)
for(i in 1:nrow(xx)){
  out=100*BinomCI(x = xx$Fail[i], n = xx$N[i],method = 'jeffreys')
  lines(rep(i,2), out[2:3])
  
  out=100*BinomCI(x = xx$`Strong Fail`[i], n = xx$N[i],method = 'jeffreys')
  lines(rep(i,2)+.2, out[2:3],col='red')
}
axis(1, at=1:nrow(xx), labels = gsub(pattern = '+',replacement = '\n+',x = xx$ARM,fixed = T),
     las=2,cex.axis=1)
points(1:nrow(xx)+.2, xx$`Percent Strong Fail`,col='red',pch=16)
```

### *stan model of cure*

*compile model*

```{r stan_model}
file1 <- file.path("Stan_models/chagas_efficacy_model_CT_values_v5.stan")
mod1 <- stan_model(file1)

Nchains=4
N_iter=2000
N_thin = Nchains
RE_RUN_STAN_MODEL=F
```

*how often do 2+ come from the same sample?*

```{r}
double_pos = pcr_chagas %>%
  filter(!is.na(CT))%>%
  group_by(USUBJID, Day_frm_rand) %>%
  mutate(MBREFID_perm = gtools::permute(MBREFID),
         N_pos = sum(CT<40)) %>% 
  filter(N_pos==2) %>%
  mutate(N_blood_draws = length(unique(MBREFID[which(CT<40)])),
         N_blood_draws_perm = length(unique(MBREFID_perm[which(CT<40)]))) %>%
  distinct(USUBJID, Day_frm_rand, .keep_all = T)

table(double_pos$N_pos)
table(double_pos$N_blood_draws)
table(double_pos$N_blood_draws_perm)
```

### *PLACEBOS fit*

Fit to placebo data from both trials

```{r all_placebo}
pcr_stan = get_analysis_dataset(dat = pcr_chagas,
                                arms_select = 'PLACEBO',
                                analysis_IDs = dat_summary$USUBJID,
                                max_PCR_replicates = 3)
data_list_stan =
  make_stan_dataset_model_quant(pcr_chagas_ss_input = pcr_stan,
                                p_1_beta_prior = .5)

fname='stan_out/all_placebos.rds'
# about 10 mins to run
if(RE_RUN_STAN_MODEL | !file.exists(fname)){
  fit_1 <- sampling(mod1, data = data_list_stan,
                    chains = Nchains,iter=N_iter,
                    thin=N_thin, verbose=T)
  save(fit_1, file = fname)
} else {
  load(fname)
}
traceplot(fit_1, pars = c('sigma_PCR',
                          'sigma','alpha_PCR',
                          'CT_pop_baseline',
                          'CT_sigma_pop_baseline',
                          'sigma_trt_all',
                          'lambda_trt','p_1'))
plot(fit_1, pars='p_1')
plot(fit_1, pars='lambda_trt')
```

### analyses of treatment arms

using per protocol population 2 (based on duration)

```{r}
pp_ids = dat_summary$USUBJID[dat_summary$PP_pop2]

label_change = c("p_1[1]" ="BNZ 300mg 8wks",
                 "p_1[2]" ="BNZ 300 wkly + E1224",
                 "p_1[3]" ="BNZ 300mg 4wks",
                 "p_1[4]" ="BNZ 150mg 4wks",
                 "p_1[5]" ="BNZ 150mg 4wks + E1224",
                 "p_1[6]" ="BNZ 300mg 2wks",
                 "p_1[7]" ="E1224 HD 4W",
                 "p_1[8]" ="E1224 HD 8W",
                 "p_1[9]" ="E1224 LD 8W")
```

All BENDITA data -

```{r bendita_stan_model}
arms_bendita = c('PLACEBO',
                 'BNZ 300MG 8W',
                 'BNZ 300MG/WK + E1224 300MG 8W',
                 'BNZ 300MG 4W',
                 "BNZ 150MG 4W",
                 "BNZ 150MG 4W + E1224 300MG 8W",
                 'BNZ 300MG 2W')
pcr_stan = get_analysis_dataset(dat = pcr_chagas %>% filter(STUDYID=='BENDITA'),
                                arms_select = arms_bendita, 
                                analysis_IDs = pp_ids,
                                max_PCR_replicates = 3)
data_list_stan = 
  make_stan_dataset_model_quant(pcr_chagas_ss_input = pcr_stan, 
                                p_1_beta_prior = .5,plot_data = T)
writeLines(sprintf('Fitting the model to data from %s individuals, with %s unique timepoints and %s treatment arms',
                   data_list_stan$N,
                   data_list_stan$Tmax,
                   data_list_stan$Trt_max))
fname='stan_out/bendita_pp2.rds'
# 35 mins to run
if(RE_RUN_STAN_MODEL | !file.exists(fname)){
  fit_1 <- sampling(mod1, data = data_list_stan,
                    chains = Nchains,iter=N_iter,
                    thin=N_thin, verbose=T)
  save(fit_1, file = fname)
} else {
  load(fname)
}

traceplot(fit_1, pars = c('sigma_PCR',
                          'sigma','alpha_PCR',
                          'CT_pop_baseline',
                          'CT_sigma_pop_baseline',
                          'sigma_trt_all','lambda_trt','p_1'))
plot(fit_1, pars='p_1')
plot(fit_1, pars='lambda_trt')
```

All E1224 data

```{r e1224_stan_model}
arms_e1224 = c('PLACEBO',
               'BNZ 300MG 8W',
               "E1224 400MG 4W",
               "E1224 400MG 8W",
               "E1224 200MG 8W")
pcr_stan = get_analysis_dataset(dat = pcr_chagas  %>% filter(STUDYID=='E1224'),
                                arms_select = arms_e1224, 
                                analysis_IDs = dat_summary$USUBJID,
                                max_PCR_replicates = 3,EOT_delta = 0)
data_list_stan = 
  make_stan_dataset_model_quant(pcr_chagas_ss_input = pcr_stan, 
                                p_1_beta_prior = .5)
writeLines(sprintf('Fitting the model to data from %s individuals, with %s unique timepoints and %s treatment arms',
                   data_list_stan$N,
                   data_list_stan$Tmax,
                   data_list_stan$Trt_max))

fname='stan_out/e1224_pp2.rds'
# about 40 mins to run
if(RE_RUN_STAN_MODEL | !file.exists(fname)){
  fit_1 <- sampling(mod1, data = data_list_stan,
                    chains = Nchains,iter=N_iter,
                    thin=N_thin, verbose=T)

  save(fit_1, file = fname)
} else {
  load(fname)
}

traceplot(fit_1, pars = c('sigma_PCR',
                          'sigma','alpha_PCR',
                          'CT_pop_baseline',
                          'CT_sigma_pop_baseline',
                          'sigma_trt_all','lambda_trt','p_1'))
plot(fit_1, pars='p_1')
plot(fit_1, pars='lambda_trt')
```

All data! Per protocol analysis

```{r all_data_model_PP}
arms_all = union(arms_bendita, arms_e1224) 
pcr_stan = get_analysis_dataset(dat = pcr_chagas,
                                arms_select = arms_all, 
                                analysis_IDs = pp_ids,
                                max_PCR_replicates = 3)
data_list_stan = 
  make_stan_dataset_model_quant(pcr_chagas_ss_input = pcr_stan, 
                                p_1_beta_prior = .5)
writeLines(sprintf('Fitting the model to data from %s individuals, with %s unique timepoints and %s treatment arms',
                   data_list_stan$N,
                   data_list_stan$Tmax,
                   data_list_stan$Trt_max))

fname='stan_out/all_data_PP.rds'
if(RE_RUN_STAN_MODEL | !file.exists(fname)){
  fit_1 <- sampling(mod1, data = data_list_stan,
                    chains = Nchains,iter=2000, 
                    thin=N_thin, verbose=T,
                    pars='CT_t_j',include=F)
  
  save(fit_1, file = fname)
} else {
  load(fname)
}

p_1_estimates = summary(fit_1, pars='p_1')$summary
rownames(p_1_estimates)=arms_all
round(p_1_estimates[, c('2.5%','50%','97.5%')]*100, 1)
my_pars = c('sigma_PCR',
            'sigma','alpha_PCR',
            'CT_pop_baseline',
            'CT_sigma_pop_baseline',
            'sigma_trt_all','lambda_trt','p_1')
traceplot(fit_1, pars = my_pars)
xx_all = as.matrix(fit_1) 
xx = xx_all[, c(grep('p_1',x = colnames(xx_all)),grep('lambda_trt',x = colnames(xx_all)))]
xx_CT_t = colMeans(xx_all[, grep('CT_t[',x = colnames(xx_all),fixed = T)])
xx_CT = colMeans(xx_all[, grep('CT_i_t[',x = colnames(xx_all),fixed = T)])
rm(xx_all)
names(arms_all) = paste('p_1[',1:length(arms_all),']',sep = '')
arms_all = gsub(pattern = '+',replacement = '\n',fixed = T,x = arms_all)
mcmc_intervals(xx, regex_pars='p_1')+theme_minimal()+
  scale_y_discrete(labels = arms_all)+
  labs(title = "Probability of cure")

names(arms_all) = paste('lambda_trt[',1:length(arms_all),']',sep = '')
mcmc_intervals(xx, regex_pars='lambda_trt')+theme_minimal()+
  scale_y_discrete(labels = arms_all)+
  labs(title = "Reduction in parasite load (Ct)")

plot_individual_fits(data_list_stan = data_list_stan,xx_CT_t = xx_CT_t,xx_CT = xx_CT,f_out = 'model_fits_all_PP.pdf')
```

```{r all_data_model_ITT}
pcr_stan = get_analysis_dataset(dat = pcr_chagas,
                                arms_select = NA, 
                                analysis_IDs = NA,
                                max_PCR_replicates = 3)
unique(pcr_stan$ARM)
data_list_stan = 
  make_stan_dataset_model_quant(pcr_chagas_ss_input = pcr_stan, 
                                p_1_beta_prior = .5)
writeLines(sprintf('Fitting the model to data from %s individuals, with %s unique timepoints and %s treatment arms',
                   data_list_stan$N,
                   data_list_stan$Tmax,
                   data_list_stan$Trt_max))
arms_all = levels(data_list_stan$pcr_chagas_ss$ARM)
fname='stan_out/all_data_ITT.rds'
if(RE_RUN_STAN_MODEL | !file.exists(fname)){
  fit_1 <- sampling(mod1, data = data_list_stan,
                    chains = Nchains,iter=2000, 
                    thin=N_thin, verbose=T,
                    pars='CT_t_j',include=F)
  save(fit_1, file = fname)
} else {
  load(fname)
}

p_1_estimates = summary(fit_1, pars='p_1')$summary
rownames(p_1_estimates)=arms_all
round(p_1_estimates[, c('2.5%','50%','97.5%')]*100, 1)
my_pars = c('sigma_PCR',
            'sigma','alpha_PCR',
            'CT_pop_baseline',
            'CT_sigma_pop_baseline',
            'sigma_trt_all','lambda_trt','p_1')
traceplot(fit_1, pars = my_pars)
xx_all = as.matrix(fit_1) 
xx = xx_all[, c(grep('p_1',x = colnames(xx_all)),grep('lambda_trt',x = colnames(xx_all)))]
xx_CT_t = colMeans(xx_all[, grep('CT_t[',x = colnames(xx_all),fixed = T)])
xx_CT = colMeans(xx_all[, grep('CT_i_t[',x = colnames(xx_all),fixed = T)])
rm(xx_all)
names(arms_all) = paste('p_1[',1:length(arms_all),']',sep = '')
arms_all = gsub(pattern = '+',replacement = '\n',fixed = T,x = arms_all)
mcmc_intervals(xx, regex_pars='p_1')+theme_minimal()+
  scale_y_discrete(labels = arms_all)+
  labs(title = "Probability of cure")

names(arms_all) = paste('lambda_trt[',1:length(arms_all),']',sep = '')
mcmc_intervals(xx, regex_pars='lambda_trt')+theme_minimal()+
  scale_y_discrete(labels = arms_all)+
  labs(title = "Reduction in parasite load (Ct)")

plot_individual_fits(data_list_stan = data_list_stan,xx_CT_t = xx_CT_t,xx_CT = xx_CT,f_out = 'model_fits_all_ITT.pdf')

```
